### 2015-07-02 doc/thesis/system.tex
Minor fixes to the section about projection types

%The rules for declaring variadic functions and recursive functions
%are similar to \textsc{T-FUNCTION1}, and we will not
%show them in this section for brevity.

@@

Lua programmers often overload the return type of functions to denote errors,
and our type system uses projection types to handle this idiom.

@@

After assigning projection types to $q$ and $r$, reading $q$ will
use the projection type $\pi_{1}^{x}$ to project the type of $q$
into the union type $\Integer \cup \Nil$, while reading $r$ will
use the projection type $\pi_{2}^{x}$ to project the type of $r$
into the union type $\Integer \cup \String$.
Now, we may want to discriminate these variables to check whether
the function call returned with success.

Introducing a projection variable $x$ in the projection environment allows our
type system to discriminate projection types $\pi_{i}^{x}$.
The rule \textsc{T-IF3} shows the case where our type system
discriminates a projection type based on the tag \texttt{nil}:
\[
\begin{array}{c}
\mylabel{T-IF3}\\
\dfrac{\begin{array}{c}
       \env_{1}(id) = \pi_{i}^{x}\\
       S_{t} = fonilpt(\penv(x), i) \;\;\;
       S_{e} = finilpt(\penv(x), i) \\
       \env_{1}, \penv[x \mapsto S_{t}] \vdash s_{1}, \env_{2} \;\;\;
       \env_{1}, \penv[x \mapsto S_{e}] \vdash s_{2}, \env_{3}\\
       \env_{4} = join(\env_{2}, \env_{3})
      \end{array}}
      {\env_{1}, \penv \vdash \mathbf{if} \; id \; \mathbf{then} \; s_{1} \; \mathbf{else} \; s_{2}, \env_{4}}
\end{array}
\]

>>>>

The rules for declaring variadic functions and recursive functions
are similar to \textsc{T-FUNCTION1}, and we will not
show them in this section for brevity.

@@

Lua programmers often overload the return type of functions to denote errors,
returning \texttt{nil} and an error message in case of error instead of
the usual return values, and our type system uses projection types to handle this idiom.

@@

After assigning projection types to $q$ and $r$, reading $q$ will
use the projection type $\pi_{1}^{x}$ to project the type of $q$
into the union type $\Integer \cup \Nil$, while reading $r$ will
use the projection type $\pi_{2}^{x}$ to project the type of $r$
into the union type $\Integer \cup \String$.
Our type system defines this behavior through rule \textsc{T-IDREAD4},
which uses the auxiliary function \emph{proj} to project an
union of second-level types into an union of first-level types:
\[
\begin{array}{c}
\mylabel{T-IDREAD4}\\
\dfrac{\env_{1}(id) = \pi_{i}^{x}}
      {\env_{1}, \penv \vdash id:proj(\penv(x), i), \env_{1}}
\end{array}
\]

Now, we may want to discriminate $q$ and $r$ to check whether
the function call returned with success.
Introducing a projection variable $x$ in the projection environment allows our
type system to discriminate projection types $\pi_{i}^{x}$,
as they are a general way to not compromise the depency between
the types of $q$ and $r$ after discriminating one of them,
so flow typing can narrow the type of both variables by testing
just one of them because the projection types of both variables
bound to the same projection variable.
The rule \textsc{T-IF3} shows the case where our type system
discriminates a projection type based on the tag \texttt{nil}:
\[
\begin{array}{c}
\mylabel{T-IF3}\\
\dfrac{\begin{array}{c}
       \env_{1}(id) = \pi_{i}^{x}\\
       S_{t} = fonilpt(\penv(x), i) \;\;\;
       S_{e} = finilpt(\penv(x), i) \\
       \env_{1}, \penv[x \mapsto S_{t}] \vdash s_{1}, \env_{2} \;\;\;
       \env_{1}, \penv[x \mapsto S_{e}] \vdash s_{2}, \env_{3}\\
       \env_{4} = join(\env_{2}, \env_{3})
      \end{array}}
      {\env_{1}, \penv \vdash \mathbf{if} \; id \; \mathbf{then} \; s_{1} \; \mathbf{else} \; s_{2}, \env_{4}}
\end{array}
\]
